\section{Introduction}
\label{sec:introduction}

Competitive indoor percussion is a judged music-and-movement activity. An
ensemble performs a designed show that combines percussion music with staged
movement and visual composition. Judges evaluate the
show across scored dimensions, called \emph{captions}: Music and Visual address
the composition and performance quality, while Music Effect and Visual Effect address
how successfully the design and performance communicate and sustain an overall
impact~\cite{wgi2026scoresheets}. These scores are expert adjudications rather
than objectively measurable outcomes: there is no distance run, time recorded,
or weight lifted.

Ensembles typically refine, complete, and improve the same show as they progress
from early-season regional competitions toward championships. This structure
raises a natural forecasting question: how much of an ensemble's eventual
championship outcome is already visible at its first competitive appearance?

The Southern California Percussion Alliance (SCPA) organizes a regional
competition circuit serving Southern California. Each SCPA season runs from
late winter through spring, culminating in a championship event. We use SCPA
as a test case for studying the internal consistency of competitive percussion
adjudication across a season.

We frame the prediction task as a test of \emph{scoring-system
predictability}: given only an ensemble's debut scores and contextual
features, how well can a model reproduce the championship subtotal (the
combined caption score before timing penalties) that expert adjudicators later
assign? Accurate forecasting implies that debut adjudication is meaningfully
continuous with championship adjudication; it
does not imply that debut scores cause later performance, that the scores are
artistically correct, or that the forecasts should guide consequential
ensemble decisions.

The contributions of this paper are: (1)~a reproducible historical SCPA
scoring database built from public CompetitionSuite competition
records~\cite{scpadb2026, csparse2026}; (2)~a leakage-controlled
debut-to-championship prediction task with chronological held-out evaluation
on the 2025--2026 seasons; and (3)~error analysis examining where the scoring
system is most and least predictable across competitive class divisions.
