\section{Predictive Task and Methods}
\label{sec:methods}

Each ensemble-season in the modeling cohort represents one performing ensemble
observed during one SCPA season and competing in one class.

\subsubsection*{Target} The primary target is the terminal championship subtotal
score on the 0--100 scale, observed at the furthest championship stage the
ensemble reached (finals, semifinals, or prelims). A secondary target (the
ensemble's class-relative championship percentile) is evaluated separately
and not mixed into the primary comparison. All point predictions and
prediction-interval endpoints are clipped to $[0, 100]$.

\subsubsection*{Features} All features are derived from the debut performance and
its context, with no information from later in the season. The debut subtotal
score, timing variables (week, day of week), class membership, competition
context (number of ensembles in the event and competition-week index),
normalized score-profile subcaptions (finer-grained sub-scores within each caption, such as composition and performance within the Music caption, standardized among ensembles evaluated
by the same judge, event, class, and subcaption), and prior-history variables
(previous championship subtotal, number of prior seasons) are included.
Imputation, scaling, and categorical encoding are fitted inside each training
fold to prevent leakage. No post-debut score, championship attendance,
championship stage, or future-season information enters as a feature.

\subsubsection*{Baselines} Three primary baselines are evaluated: (1)~the global
training median; (2)~the debut-class training median with a global fallback
for unseen classes; and (3)~the debut score itself as a direct point
prediction. The identity baseline reveals the raw continuity of debut scores
relative to championship scores. A secondary baseline that predicts the
debut-class percentile directly is evaluated on the percentile target only
and is not included in the primary score table.

\subsubsection*{Models} Ridge regression is trained with fold-fitted imputation,
standard scaling, and one-hot class encoding; the L2 penalty is tuned by
development cross-validation. The selected Ridge penalty is $\alpha=10$.
A gradient boosting model is tuned over a predeclared grid; the selected model
uses 200 estimators, learning rate 0.05, maximum depth 3, and minimum leaf size
10. Stochastic procedures use random seed 42.

\subsubsection*{Validation} Development validation uses an expanding-season
scheme: the model trained on 2017 predicts 2018, then successively adds
seasons through 2024. The headline model is selected by development
cross-validation MAE (Ridge: 2.769; GBM: 2.798), not by holdout performance.
The 2025--2026 seasons are held out completely and used only for final
evaluation.

\subsubsection*{Ablation} Six feature sets are evaluated sequentially to quantify
each block's marginal contribution: (A)~debut subtotal only; (B)~add debut
penalty, timing, and class; (C)~add competition context; (D)~add normalized
score profile and missingness indicators; (E)~add prior-history variables;
(F)~add prior class and class-change direction (upward, downward, or unchanged
from the previous observed season). Each block adds only the indicated features
to the previous set.
