\section{Results}
\label{sec:results}

\input{tables/tab_holdout_metrics}

Table~\ref{tab:holdout-metrics} reports held-out evaluation metrics for all
models on the 2025--2026 seasons ($n = 207$). The global-median baseline
achieves an MAE of 5.858 and an $R^2$ near zero, consistent with constant
predictions. The class-median baseline substantially improves on it (MAE
4.767, Spearman $\rho = 0.568$), confirming that class membership carries
predictive information beyond a global constant. The debut-score identity
baseline preserves meaningful rank ordering (Spearman $\rho = 0.733$) but
severely underpredicts terminal scores, with a mean residual of $-11.224$
points; ensembles improve considerably between debut and championship, so the
raw debut score is a poor terminal-score forecast.

Ridge regression achieves a held-out MAE of 2.676 (RMSE 3.499, $R^2 = 0.769$,
Spearman $\rho = 0.892$). Ridge was selected as the headline model by
development cross-validation MAE (2.769) rather than by post-hoc holdout
comparison. A cluster bootstrap 95\% confidence interval for the
difference GBM MAE $-$ Ridge MAE is $[0.056, 0.454]$ (2,000 resamples, clustered by ensemble identity), confirming that Ridge
outperforms gradient boosting on this evaluation. Gradient boosting's weaker
held-out performance is consistent with the structure of the task: the ablation
and Ridge coefficient analysis both indicate that debut subtotal and class
membership account for most of the predictive signal, leaving little residual
structure for an ensemble method to exploit. At 574 development observations,
the added complexity of gradient boosting does not recover additional signal
over Ridge. An empirical prediction
interval formed by adding and subtracting the development residual 90th
percentile (5.795 points) covers 87.9\% of held-out outcomes.
Figure~\ref{fig:predicted-vs-observed} shows predicted versus observed
subtotals for the Ridge model.

\input{figures/fig_predicted_vs_observed}

\input{tables/tab_ablation}

Table~\ref{tab:ablation} reports development cross-validation MAE for each
ablation step. Adding debut timing and class (B) produces the largest
single-step improvement. Competition context (C) adds further gain; the
score-profile block (D) does not improve over C at this sample size; prior
history (E) recovers the gap; and explicit class-change direction (F)
adds no further improvement. Figure~\ref{fig:ridge-coefficients} shows the 15
largest Ridge coefficients by absolute magnitude. PIA (the lowest-tier
independent class) is the regression reference category; this choice scales
coefficient magnitudes relative to that baseline but does not affect model
predictions or any reported metric. Debut subtotal and class membership are
the dominant predictors; prior championship subtotal adds incremental signal.

\input{tables/tab_holdout_by_class}

Table~\ref{tab:holdout-by-class} disaggregates held-out MAE and residuals by
class. PSA (Scholastic A) has the highest class-level MAE (3.254 across 112
held-out observations, 54.1\% of the holdout). Its near-zero median residual
($+0.087$), widest terminal-score (SD 6.764) and residual (SD 4.101)
distributions, and large errors in both directions indicate heterogeneous
development rather than systematic overprediction. PSA supplies eight of the
ten largest positive residuals, partly reflecting its sample size.

\input{figures/fig_ridge_coefficients}
